Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

\todo{Rahul's result? No. Do it in later sections}

@@

>>>>

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-0mm}}
\def\figcapdown{\vspace{-0mm}}

@@

@@

\section{H-V Multiway Spatial Joins} \label{sec:hv}

This section deals with a special version of the $k$-SJ problem. Recall that the input of $k$-SJ comprises $k$ sets of rectangles: $R_1, R_2, ..., R_k$. In the special version --- which we name the {\em H-V $k$-SJ} problem ---  we impose the constraints that (i) $k \ge 3$, (ii) $R_{k-1}$ should be a set of horizontal segments, and (iii) $R_k$ should be a set of vertical segments. For better clarity, we will represent the input sets as $R_1, R_2, ..., R_{k-2}, H$ ($=R_{k-1}$), and $V$ ($=R_k$). Remember that each $R_i$ ($i \in [k-2]$) is a set of rectangles. As we will see in the next section, solving the H-V $k$-SJ problem is an imperative step for settling the original $k$-SJ problem.

Our objective is to prove that the H-V $k$-SJ problem can be reduced to the $(k-1)$-SJ problem --- note: it is $(k-1)$-SJ here, rather than H-V $(k-1)$-SJ. For this purpose, we assume the existence of an algorithm $\A$ that can solve $\kappa$-SJ problems for all $\kappa \in [2, k-1]$. Denote by $F_\kappa(n, \out)$ the worst-case runtime of $\A$ when it is executed on any instance of $\kappa$-SJ that has input size $n$ and output size $\out$. We consider that $F_\kappa(n, \out) \le F_{\kappa + 1}(n, \out)$ for any $\kappa \in [2, k-2]$, that is, its efficiency on $\kappa$-SJ should not be worse than that on $(\kappa+1)$-SJ.

\todo{Remark on Rahul's result}
